Untitled Draft

### 2023-03-15 doc/manuscript.Rmd
Add PA tables and tidy Rmd

```{r load-targets, include=FALSE}
tar_load(data_clean)
tar_load(purdy_pictures)
tar_load(model_tables)
pretty <- function(x) format(x, big.mark = ",")
```

@@

```{r demo-participants}
tar_load(demog_table)
tar_load(table_1) # to get participants data

tar_load(demog_table)

papaja::apa_table(demog_table,
  caption = "Participant characteristics",
  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"),
  landscape = TRUE,
  col_spanners = list("Age group" = c(2, 6))
)
```

@@

We estimated the effect of sleep duration on physical activity by age. Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-duration) and Figure \@ref(fig:PA-by-sleep-duration-fig).
As age increases, both physical activity volume and intensity decrease.
We found a subtle inverted U-shaped relationship between average sleep duration and physical activity volume, where the highest volume of physical activity was linked to average sleep duration.

```{r PA-by-sleep-duration}
# var_names <- c(
#   "scale_pa_volume by scale_sleep_duration_lag",
#   "scale_pa_intensity by scale_sleep_duration_lag"
# )

# PA_by_sleep_duration <- lapply(model_list[var_names], function(x) {
#   tab <- format_table(x$table)
#   tab
# })

# names(PA_by_sleep_duration) <- gsub("scale_", "", names(PA_by_sleep_duration)) |>
#   gsub("\\sby.*", "", x = _) |>
#   gsub("_", " ", x = _) |>
#   fix_model_names()

# papaja::apa_table(PA_by_sleep_duration,
#   caption = "Physical activity  by sleep duration controlling for SES, gender and BMI",
#   note = note,
#   escape = FALSE
# )
```

@@

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-efficiency) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
We did not find a relationship between physical activity volume and sleep efficiency.
However, there was a subtle U-shaped relationship where individuals with above-average sleep efficiency engaged in more intense physical activity.

```{r PA-by-sleep-efficiency}
# var_names <- c(
#   "scale_pa_volume by scale_sleep_efficiency_lag",
#   "scale_pa_intensity by scale_sleep_efficiency_lag"
# )

# PA_by_sleep_efficiency <- lapply(model_list[var_names], function(x) {
#   tab <- format_table(x$table)
#   tab
# })

# names(PA_by_sleep_efficiency) <- gsub("scale_", "", names(PA_by_sleep_efficiency)) |>
#   gsub("\\sby.*", "", x = _) |>
#   gsub("_", " ", x = _) |>
#   fix_model_names()

# papaja::apa_table(PA_by_sleep_efficiency,
#   caption = "Physical activity by sleep efficiency controlling for SES, gender and BMI",
#   note = note,
#   escape = FALSE
# )
```

@@

We estimated the effect of sleep onset on physical activity by age. Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-onset) and Figure \@ref(fig:PA-by-sleep-onset-fig).
There were strong U-shaped relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.

```{r PA-by-sleep-onset}
# var_names <- c(
#   "scale_pa_volume by scale_sleep_onset_lag",
#   "scale_pa_intensity by scale_sleep_onset_lag"
# )

# PA_by_sleep_onset <- lapply(model_list[var_names], function(x) {
#   tab <- format_table(x$table)
#   tab
# })

# names(PA_by_sleep_onset) <- gsub("scale_", "", names(PA_by_sleep_onset)) |>
#   gsub("\\sby.*", "", x = _) |>
#   gsub("_", " ", x = _) |>
#   fix_model_names()

# papaja::apa_table(PA_by_sleep_onset,
#   caption = "Physical activity by sleep onset controlling for SES, gender and BMI",
#   note = note,
#   escape = FALSE
# )
```

@@

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:PA-by-sleep-regularity) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
There was a U-shaped relationship between sleep regularity and physical activity volume.
Participants with below-average sleep regularity tended to have average physical activity volume.
Increases in regularity above the average were linked to greater physical activity volume.
There was a strong linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
Greater sleep regularity was associated with greater physical activity the following day.

```{r PA-by-sleep-regularity}
# var_names <- c(
#   "scale_pa_volume by scale_sleep_regularity_lag",
#   "scale_pa_intensity by scale_sleep_regularity_lag"
# )

# PA_by_sleep_regularity <- lapply(model_list[var_names], function(x) {
#   tab <- format_table(x$table)
#   tab
# })

# names(PA_by_sleep_regularity) <- gsub("scale_", "", names(PA_by_sleep_regularity)) |>
#   gsub("\\sby.*", "", x = _) |>
#   gsub("_", " ", x = _) |>
#   fix_model_names()

# papaja::apa_table(PA_by_sleep_regularity,
#   caption = "Physical activity by sleep regularity controlling for SES, gender and BMI",
#   note = note,
#   escape = FALSE
# )
```

>>>>

```{r load-targets, include=FALSE}
tar_load(data_clean)
tar_load(purdy_pictures)
tar_load(model_tables)
tar_load(demog_table)
tar_load(table_1)
pretty <- function(x) format(x, big.mark = ",")
```

@@

```{r demo-participants}
papaja::apa_table(demog_table,
  caption = "Participant characteristics",
  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"),
  landscape = TRUE,
  col_spanners = list("Age group" = c(2, 6))
)
```

@@

We estimated the effect of sleep duration on physical activity by age. Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
As age increases, both physical activity volume and intensity decrease.
We found a subtle inverted U-shaped relationship between average sleep duration and physical activity volume, where the highest volume of physical activity was linked to average sleep duration.

```{r pa-outcomes}
papaja::apa_table(
  model_tables$physical_activity$data,
  caption = model_tables$physical_activity$caption,
  note = model_tables$physical_activity$note,
  col_spanners = model_tables$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

@@

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
We did not find a relationship between physical activity volume and sleep efficiency.
However, there was a subtle U-shaped relationship where individuals with above-average sleep efficiency engaged in more intense physical activity.

@@

We estimated the effect of sleep onset on physical activity by age. Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
There were strong U-shaped relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.

@@

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
There was a U-shaped relationship between sleep regularity and physical activity volume.
Participants with below-average sleep regularity tended to have average physical activity volume.
Increases in regularity above the average were linked to greater physical activity volume.
There was a strong linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
Greater sleep regularity was associated with greater physical activity the following day.
